TITLE

### 2021-02-23 outputs/Paper.Rmd
Appendix Update

---
title: "TITLE"
author: "Adrian Wong, Yingying Zhou, Xinyi Xu, Yang Wu "
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 bookdown::pdf_document2:
 toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
bibliography: references.bib
---

@@

library(tidyverse)
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")

@@

>>>>

---
title: "TITLE"
author: "Adrian Wong, Yingying Zhou, Xinyi Xu, Yang Wu "
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 bookdown::pdf_document2:
 toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
---

@@

library(tidyverse)
```

@@

\newpage
# Appendix

## Appendix A
```{r AppendixA, message=FALSE, echo = FALSE}
### Number in GTA ### 
number_of_Toronto = 7500
number_of_Durham = 3260
number_of_York = 5553
number_of_Peel = 6235
number_of_Halton = 2803
number_of_GTA = sum(number_of_Toronto,number_of_Durham,number_of_York,number_of_Peel,number_of_Halton)

### Proportion ###
proportion_Toronto = (number_of_Toronto/number_of_GTA*100) 
proportion_Durham = (number_of_Durham/number_of_GTA*100)
proportion_York = (number_of_York/number_of_GTA*100)
proportion_Peel = (number_of_Peel/number_of_GTA*100)
proportion_Halton = (number_of_Halton/number_of_GTA*100)
Proportion_GTA = (number_of_GTA /number_of_GTA*100)

### Number of Sample ###
number_of_sample = 1637

sample_Toronto =proportion_Toronto*number_of_sample
sample_Durham =proportion_Durham *number_of_sample
sample_York =proportion_York*number_of_sample
sample_Peel =proportion_Peel*number_of_sample
sample_Halton =proportion_Halton *number_of_sample

### Dataframe ###
sample_size <- data.frame(
  Region = c ("Toronto", "Durham" , "York" , "Peel" , "Halton","Total"),
  Number_of_Region = c (number_of_Toronto,number_of_Durham,number_of_York,number_of_Peel,number_of_Halton,number_of_GTA),
  Proportion_of_Region= c (proportion_Toronto,proportion_Durham,proportion_York,proportion_Peel,proportion_Halton,Proportion_GTA)%>% round(digits = 2),
  Sample_of_Region = c (sample_Toronto,sample_Durham,sample_York ,sample_Peel,sample_Halton,number_of_sample) %>% round(digits = 0)
  )

### Table ###
library(kableExtra)
sample_size %>% 
  knitr::kable(caption = "Detailed information for stratification",
               col.names = c("Region", "Number of Restuarants", "Proportion(%)", "Sample Selected"))%>%
  kable_styling()
```

## Appendix B
```{r AppendixB, message=FALSE, echo = FALSE}
### basic information ###
number_of_survey = 3454
number_of_consent = 11325

print_cost_per_page = 0.05 
envelope_cost = 0.15
one_way_stamp = 0.55

### Calculation ###

total_print_cost = print_cost_per_page* (number_of_consent+number_of_survey)
total_envelope_cost = (number_of_consent+number_of_survey)*envelope_cost*2
total_stamp_cost =(number_of_consent+number_of_survey)*one_way_stamp*2

total_cost = total_print_cost+total_envelope_cost+total_stamp_cost

### dataframe ###
estimated_cost <- data.frame(
  Components = c ("Printing Cost", "Envelope Cost", "Stamp Cost"),
  Cost_per_unit= c (print_cost_per_page,envelope_cost,one_way_stamp),
  Total_cost_of_each_component  = c (total_print_cost, total_envelope_cost, total_stamp_cost)
)

### Table  ###
library(kableExtra)
estimated_cost %>% 
  knitr::kable(caption = "Estimated Cost",
               col.names = c("Components", "Cost per unit", "Total cost for each component"))%>%
  kable_styling()
